```{r, message=FALSE, echo=FALSE, results="hide"}
# Setup
library(knitr)
library(captioner)
library(dplyr)

if (!exists("tables")) { tables <- captioner(prefix="Table") }
if (!exists("figures")) { figures <- captioner(prefix="Figure") }
figures("primers_count", 
        paste("Count of assigned primers.",
              "The bar height indicates the total reads assigned to the given primer,
               stacked for those under the error rate threshold (Pass) and
               over the threshold (Fail)."))
figures("primers_hist", 
        paste("Distribution of primer match error rates.",
              "The error rate is the percentage of mismatches between the primer sequence and the 
               read for the best matching primer. The dotted line indicates the error threshold used."))
figures("primers_error", 
        paste("Distribution of primer match error rates,",
              "broken down by assigned primer. The error rate is the percentage of mismatches between the 
               primer sequence and the read for the best matching primer. The dotted line indicates the error
               threshold used."))
```

```{r, echo=FALSE}

#' Plot MaskPrimer log table
#'
#' @param    ...        data.frames returned by loadLogTable to plot.
#' @param    titles     vector of titles for each log in ...; 
#'                      if NULL the titles will be empty.
#' @param    style      type of plot to draw. One of:
#'                      \itemize{
#'                        \item \code{"histogram"}:  total error distribution
#'                        \item \code{"count"}:      count of matches for each primer
#'                        \item \code{"error"}:      error distributions for each primer
#'                        \item \code{"position"}:   distribution of start positions by primer
#'                                                   for matches >= max_error.
#'                      }
#' @param    max_error  error threshold to used to determing whether a primer match is valid.
#' @param    sizing     defines the style and sizing of the theme. One of 
#'                      \code{c("figure", "window")} where \code{sizing="figure"} is appropriately
#'                      sized for pdf export at 7 to 7.5 inch width, and \code{sizing="window"}
#'                      is sized for an interactive session.
#'                  
#' @return   NULL
#' 
#' @family   pRESTO log plotting functions
#' 
#' @export
plotMaskPrimers <- function(..., titles=NULL, style=c("histogram", "count", "error", "position"),
                            max_error=0.3, sizing=c("figure", "window")) {
    ## DEBUG
    # c('PRIMER', 'PRSTART', 'BARCODE', 'ERROR')
    # titles=NULL
    # max_error=0.2
    # style="h"

    # Parse arguments
    style <- match.arg(style)
    sizing <- match.arg(sizing)
    log_list <- list(...)
    log_count <- length(log_list)
    
    # Define titles
    if (is.null(titles)) {
        titles <- rep("", log_count)
    } else if (length(titles) != log_count) {
        stop("You must specify one title per input log table.")
    }
    
    # Set base plot settings
    base_theme <- alakazam::baseTheme(sizing=sizing)
    
    # Define plot objects for each log table
    plot_list <- list()
    for (i in 1:log_count) {
        log_df <- log_list[[i]]
        if (style == "histogram") {
            # Check for valid log table
            check <- alakazam::checkColumns(log_df, c("ERROR"))
            if (check != TRUE) { stop(check) }
            
            # Plot total error distribution
            log_df <- dplyr::filter(log_df, !is.na(ERROR))
            p1 <- ggplot(log_df, aes(x=ERROR)) +
                base_theme +     
                ggtitle(titles[i]) +
                xlab("Error") +
                ylab("Reads") +
                scale_x_continuous(limits=c(-0.05, 1.05), breaks=seq(0.0, 1.0, 0.2)) +
                scale_y_continuous(labels=scientific_format()) + 
                geom_histogram(binwidth=0.025, colour="white", fill=PRESTO_PALETTE["blue"], 
                               linewidth=0.25, center=0) +
                geom_vline(xintercept=max_error, color=PRESTO_PALETTE["red"], linewidth=0.5, linetype=3)
        } else if (style == "count") {
            # Check for valid log table
            check <- alakazam::checkColumns(log_df, c("ERROR", "PRIMER"))
            if (check != TRUE) { stop(check) }
            
            # Set passed and failed 
            log_df$RESULT <- factor(log_df$ERROR <= max_error, 
                                    levels=c(TRUE, FALSE), 
                                    labels=c("Pass", "Fail"))
            
            # Plot primer match counts
            guide_values <- setNames(c(PRESTO_PALETTE["blue"], PRESTO_PALETTE["red"]), c("Pass", "Fail"))
            log_df <- dplyr::filter(log_df, !is.finite(PRIMER), !is.na(RESULT))
            p1 <- ggplot(log_df, aes(x=PRIMER)) +
                base_theme + 
                theme(axis.text.x=element_text(angle=45, vjust=1, hjust=1)) +
                ggtitle(titles[i]) +
                xlab("") +
                ylab("Reads") +
                scale_fill_manual(name="", values=guide_values) +
                geom_bar(aes(fill=RESULT), position="stack", width=0.7, na.rm=TRUE)
        } else if (style == "error") {
            # Check for valid log table
            if (!all(c("ERROR", "PRIMER") %in% names(log_df))) {
                stop("Log table must contain the fields 'PRIMER' and 'ERROR'.")
            } else if (all(is.na(log_df$ERROR))) {
                stop("The field 'ERROR' contains no data.")
            } else if (all(is.na(log_df$PRIMER))) {
                stop("The field 'PRIMER' contains no data.")
            }
            
            # Plot error distribution by primer
            log_df <- dplyr::filter(log_df, !is.na(ERROR), !is.na(PRIMER))
            p1 <- ggplot(log_df, aes(x=PRIMER, y=ERROR)) +
                base_theme + 
                theme(legend.position="none") +
                theme(axis.text.x=element_text(angle=45, vjust=1, hjust=1)) +
                ggtitle(titles[i]) +
                xlab("") +
                ylab("Error") +
                scale_y_continuous(limits=c(-0.05, 1.05), breaks=seq(0, 1, 0.2)) +
                geom_violin(aes(fill=PRIMER), adjust=3.0, scale="width", trim=T, width=0.7) +
                geom_errorbarh(aes(xmin=(after_stat(x)) - 0.4, xmax=(after_stat(x)) + 0.4), linewidth=1.5,
                               stat="summary", fun="mean") +
                geom_hline(yintercept=max_error, color=PRESTO_PALETTE["red"], linewidth=0.5, linetype=3)    
        } else if (style == "position") {
            # Check for valid log table
            check <- alakazam::checkColumns(log_df, c("PRIMER", "PRSTART"))
            if (check != TRUE) { stop(check) }
            
            # Plot start position by primer
            log_df <- dplyr::filter(log_df, ERROR <= max_error, !is.na(PRSTART), !is.na(PRIMER))
            p1 <- ggplot(log_df, aes(x=PRIMER, y=PRSTART)) +
                base_theme + 
                theme(legend.position="none") +
                theme(axis.text.x=element_text(angle=45, vjust=1, hjust=1)) +
                ggtitle(titles[i]) +
                xlab("") +
                ylab("Start position") +
                geom_boxplot(aes(fill=PRIMER), width=0.7)
        } else {
            stop("Nothing to plot.")
        }

        plot_list[[i]] <- p1
    }
    
    # Plot
    do.call(gridPlot, args=c(plot_list, ncol=1))
}


primer_log_1 <- loadLogTable(primer_log_file_1)
primer_log_2 <- loadLogTable(primer_log_file_2)
plot_titles <- c("Constant region primer", "V region primer")
```
\newpage
# Primer Identification

The MaskPrimers tool supports identification of multiplexed primers and UMIs.
Identified primer regions may be masked (with Ns) or cut to mitigate downstream
SHM analysis artifacts due to errors in the primer region. An annotion is added to 
each sequences that indicates the UMI and best matching primer. In the case of
the constant region primer, the primer annotation may also be used for isotype 
assignment.

## Count of primer matches

```{r, echo=FALSE, warning=FALSE}
plotMaskPrimers(primer_log_1, primer_log_2, titles=plot_titles,
                style="count", sizing="figure")
```

`r figures("primers_count")`

## Primer match error rates

```{r, echo=FALSE, warning=FALSE}
plotMaskPrimers(primer_log_1, primer_log_2, titles=plot_titles, 
                style="hist", sizing="figure")
```

`r figures("primers_hist")`

```{r, echo=FALSE, warning=FALSE}
plotMaskPrimers(primer_log_1, primer_log_2, titles=plot_titles, 
                style="error", sizing="figure")
```

`r figures("primers_error")`


```
