```{R, message=FALSE, echo=FALSE, results="hide"}
# Setup
library(knitr)
library(captioner)
if (!exists("tables")) { tables <- captioner(prefix="Table") }
if (!exists("figures")) { figures <- captioner(prefix="Figure") }
figures("headers_conscount", "Histogram showing the distribution of read counts (CONSCOUNT) for 
                              total sequences (top) and unique sequences (bottom).")
figures("headers_dupcount", "Histogram showing the distribution of unique UMI counts for 
                             all unique sequences (top) and unique sequences represented 
                             by at least two raw reads (bottom).")
figures("headers_pr1", "Percentage internal C-region annotations for total sequences.
                        Parenthetical numbers in the legend are the number of sequences.")
figures("headers_pr2", "Percentage internal C-region annotations for all unique sequences.
                        Parenthetical numbers in the legend are the number of sequences.")
figures("headers_pr3", "Percentage internal C-region annotations for unique sequences represented by at least two raw reads.
                        Parenthetical numbers in the legend are the number of sequences.")
```

```{r, echo=FALSE}
parse_log_1 <- loadLogTable(log_file_total)
parse_log_2 <- loadLogTable(log_file_unique)
parse_log_3 <- loadLogTable(log_file_atleast2)
primer_field <- "PRCONS"
```

# Summary of Final Output

Final processed output is contained in the `total`, `unique`, and `unique-atleast-2` 
files, which contain all processed sequences, unique sequences, and only those unique
sequences represented by at least two raw reads, respectively. The figures below
shown the distributions of annotations for these final output files.

## Distribution of read and UMI counts

```{r, echo=FALSE}
plotParseHeaders(parse_log_1, parse_log_2, 
                 titles=c("Total", "Unique"), 
                 style="count", primer=primer_field, count="CONSCOUNT", 
                 sizing="figure")
```

`r figures("headers_conscount")`

```{r, echo=FALSE}
plotParseHeaders(parse_log_2, parse_log_3, 
                 titles=c("Unique", "At least 2 Reads"), 
                 style="count", primer=primer_field, count="DUPCOUNT", 
                 sizing="figure")
```

`r figures("headers_dupcount")`

## C-region annotations

```{r, echo=FALSE}
plotParseHeaders(parse_log_1, titles=c("Total"), 
                 style="primer", primer=primer_field, sizing="figure")
```

`r figures("headers_pr1")`

```{r, echo=FALSE}
plotParseHeaders(parse_log_2, titles=c("Unique"), 
                 style="primer", primer=primer_field, sizing="figure") 
```

`r figures("headers_pr2")`

```{r, echo=FALSE}
plotParseHeaders(parse_log_3,  titles=c("Unique At least 2 Reads"), 
                 style="primer", primer=primer_field, sizing="figure") 
```

`r figures("headers_pr3")`
