
```{R, message=FALSE, echo=FALSE, results="hide"}
library(knitr)
library(captioner)

if (!exists("tables")) { tables <- captioner(prefix="Table") }
if (!exists("figures")) { figures <- captioner(prefix="Figure") }
figures("quality", 
        "Mean Phred quality scores. The dotted line indicates the average quality score of 20
         under which reads were removed.")
```

```{r, echo=FALSE}
#' Plot FilterSeqQuality log table
#'
#' @param    ...     data.frames returned by loadLogTable to plot
#' @param    titles  vector of titles for each log in ...; 
#'                   if NULL the titles will be empty.
#' @param    cutoff  value at which to draw a vertical line separating 
#'                   passing and failing values.
#' @param    sizing  defines the style and sizing of the theme. One of 
#'                   \code{c("figure", "window")} where \code{sizing="figure"} is appropriately
#'                   sized for pdf export at 7 to 7.5 inch width, and \code{sizing="window"}
#'                   is sized for an interactive session.
#' 
#' @return   NULL
#' 
#' @family   pRESTO log plotting functions
#' 
#' @export
plotFilterSeqQuality <- function(..., titles=NULL, cutoff=20, sizing=c("figure", "window")) {
    ## DEBUG
    # titles=NULL
    # cutoff=20

    # Parse arguments
    log_list <- list(...)
    log_count <- length(log_list)
    sizing <- match.arg(sizing)
    
    # Define titles
    if (is.null(titles)) {
        titles <- rep("", log_count)
    } else if (length(titles) != log_count) {
        stop("You must specify one title per input log table.")
    }
    
    # Set base plot settings
    base_theme <- alakazam::baseTheme(sizing=sizing)

    # Define plot objects for each log table
    plot_list <- list()
    for (i in 1:log_count) {
        log_df <- log_list[[i]]
        
        # Get count field
        log_fields <- names(log_df)
        count_field <- log_fields[log_fields %in% names(FILTER_COUNT_FIELDS)]
        if (length(count_field) < 1) {
            stop("No valid FilterSeq log field was found.")
        } else if (length(count_field) < 1) {
            stop("Too many FilterSeq log fields were found. Only one count field should be present.")
        }
        # Check count field
        check <- alakazam::checkColumns(log_df, count_field)
        if (check != TRUE) { stop(check) }
        
        # Table counts
        log_tab <- as.data.frame(table(value=floor(as.numeric(log_df[, count_field]))), 
                                 responseName="count")
        #print(log_tab)
        #log_tab$value <- as.numeric(log_tab$value)
        x_intercept <- 20
        
        #if (!"0" %in% levels(log_tab$value)) {
        #    log_tab$value <- factor(log_tab$value, levels = c("0", levels(log_tab$value)))
        #}
        log_tab$value <- as.numeric(as.character(log_tab$value))
        
        p1 <- ggplot(log_tab, aes(x=value, y=count)) +
            base_theme +     
            ggtitle(titles[i]) +
            xlab(FILTER_COUNT_FIELDS[count_field]) +
            ylab("Reads") +
            scale_x_continuous(breaks = seq(0, max(log_tab$value), by = 10), expand = c(0, 0)) + 
            scale_y_continuous(labels=scientific) + 
            #geom_histogram(fill=PRESTO_PALETTE["blue"], binwidth=1, center=0) +
            geom_bar(fill=PRESTO_PALETTE["blue"], stat="identity", width=0.95, na.rm=TRUE) +
            geom_vline(xintercept=x_intercept, color=PRESTO_PALETTE["red"], linewidth=0.5, linetype=3)

        plot_list[[i]] <- p1
    }
    
    # Plot
    do.call(gridPlot, args=c(plot_list, ncol=1))
}


quality_log <- loadLogTable(quality_log_file)
```
\newpage

# Quality Scores

Quality filtering is an essential step in most sequencing workflows. pRESTO’s
FilterSeq tool remove reads with low mean Phred quality scores. 
Phred quality scores are assigned to each nucleotide base call in automated 
sequencer traces. The quality score (`Q`) of a base call is logarithmically 
related to the probability that a base call is incorrect (`P`): 
$Q = -10 log_{10} P$. For example, a base call with `Q=30` is incorrectly 
assigned 1 in 1000 times. The most commonly used approach is to remove read 
with average `Q` below 20.

```{r, echo=FALSE}
plotFilterSeqQuality(quality_log, sizing="figure")
```

`r figures("quality")`
